\documentclass[fleqn]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{mathexam}
\usepackage{verbatim}

\ExamClass{CSCE 240}
\ExamName{Homework 4}
\ExamHead{Due: 30 March 2019}

\let
\ds
\displaystyle

\begin{document}
\ExamInstrBox {
  You shall submit a zipped, \textbf{and only zipped}, archive of your homework
  directory, hw4. The directory shall contain, at a minimum, the files
  \texttt{gradebook.cc} and \texttt{gradebook.h}. Name the archive submission
  file hw4.zip \\

  I will use my own makefile to compile and link to your \texttt{gradebook.cc}
  and \texttt{gradebook.h} files. You must submit, at least, these two files.
}
%
I was sufficiently impressed with your last effort on the GradeBook class
library, but have decided that I want to use more of the functionalities of the
C++ language. \\
%
\\
Be mindful. Sometimes the data gets corrupted and may result in empty
GradeBooks. These cases are well-defined in the method descriptions. \\
%
\\
Read the provided header file documentation for instructions on how the
functions should work. \\
%
\\
I have provided you a set of test apps which you can use to ensure that your
code is, at least partially, correct. I would suggest a more rigorous testing
scheme to ensure that your methods handle missing data. \\
%
\\
Late assignments will lose 25\% per day late, with no assignment begin accepted
after 3 days (at 100\% reduction in points).\\
\\
%
You will receive one point for each passed test as illustrated in the
test\_*.cc file. There will be an additional point for compiling against all the
tests.
\end{document}

